---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linearReg)
library(stats)
```


This introduction of 'linearReg' function will use the 'mtcars' data set built 
into R, which has 32 observations and 11 variables.

```{r, echo=F}
data=mtcars
head(mtcars)
```

To set up before implementation of 'linearReg' function:

Since we need a matrix of the explanatory variables, we will extract the 
explanatory variables into a matrix and extract a response variable vector. In 
this example, the explanatory variables of interest will be 'cyl' (number of 
cylinder), and 'wt' (weight of vehicle) and the responding variable will be 
'mpg' (Miles/(US) gallon).

```{r}
##Extract X-> select cyl (column 2) and wt (column 6) variables
X=as.matrix(mtcars[c("cyl", "wt")])

##Extract y-> mpg (column 1)
y=as.vector(mtcars["mpg"])
```

To use the function 'linearReg':

The model of interest is: mpg = B0 + B1*cyl + B2*wt

```{r}
linearReg(y,X)
```

In comparison to summary of the 'lm()' function in the stats package:

```{r}
model=lm(mpg~cyl+wt, data=mtcars)
summary(model)
```

The values within both function's outputs appear to be executed with the same 
amount of precision.


To compare the speed between 'linearReg' and 'summary(lm())':

```{r}
system.time(linearReg(y,X))
system.time(summary(model))
```

The 'linearReg' function and 'summary(lm())' function appear to similar 
efficiency with total system time elapsed to be around 0.001 seconds.