---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linearRegression)
```

This introduction of 'linearReg' function will use the 'mtcars' data set built 
into R, which has 32 observations and 11 variables.

```{r}
head(mtcars)
```

### Set up before implementation of 'linearReg' function:

Since we need a matrix of the explanatory variables, we will extract the 
explanatory variables of the data set into a matrix and the response variable 
as a vector. In this example, the explanatory variables of interest will be 
'cyl' (number of cylinder), and 'wt' (weight of vehicle) and the responding 
variable will be 'mpg' (Miles/(US) gallon).

```{r}
##Extract X-> select cyl (column 2) and wt (column 6) variables
X=as.matrix(mtcars[c("cyl", "wt")])

##Extract y-> mpg (column 1)
y=as.vector(mtcars["mpg"])
```

### Using the function 'linearReg':

The model of interest in this example is: mpg = B0 + B1*cyl + B2*wt

```{r}
linearReg(y,X)
```

### Comparison of the 'lm()' function summary to 'linearReg':

The summary of the 'lm()' function is very similar to 'linearReg' with a 
few exceptions:

1. 'linearReg' includes 95% Confidence Intervals, Variance Inflation Factor
    (VIF), and the input is a matrix and vector
    
2. 'lm()' includes Residual Standard Error and F-statistic information and 
    the input is a model formula

The summary of the 'lm()' function in the stats package for comparison:

```{r}
#original 'lm' function
model=lm(mpg~cyl+wt, data=mtcars)
summary(model)
```

The values that are shared within both function's outputs appear to be executed 
with the same amount of precision. The 'summary(lm())' function has the same 
output values as 'linearReg' only the values of the former are rounded to the
ten-thousandth decimal point. 

### Comparison of the VIF from 'linearReg' to the VIF of 'lm()' using 'vif' function in the car package:

```{r}
#VIF of 'linearReg'
linearReg(y,X)$VIF

#VIF of lm
car::vif(model)
```

The above demonstrates that the 'linearReg' function accurately estimates the 
variance inflation factors of the covariates in comparison to the 'vif' 
function. 

### To compare the efficiency between 'linearReg' and 'summary(lm())':

```{r}
system.time(linearReg(y,X))
system.time(summary(lm(mpg~cyl+wt, data=mtcars)))

bench::mark(linearReg(y,X))
bench::mark(summary(lm(mpg~cyl+wt, data=mtcars)))
```

The 'linearReg' function and 'summary(lm())' function appear to have similar 
system time elapses indicating similar efficiency. Benchmarking the functions
with 'bench::mark()' further justifies that the efficiency is comparable between
the two functions.

As stated above, 'linearReg' and 'summary(lm())' functions are very similar but
have some differences in outputs which can potentially contribute to 
small discrepancies when benchmarking the efficiency of these functions. Again,
these differences include: 'linearReg' additionally outputs 95% confidence 
intervals and variance inflation factors while 'summary(lm())' additionally
outputs residual standard error and F-statistic information.
