---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linearRegression)
```

This introduction of 'linearReg' function will use the 'mtcars' data set built 
into R, which has 32 observations and 11 variables.

```{r}
head(mtcars)
```

To set up before implementation of 'linearReg' function:

Since we need a matrix of the explanatory variables, we will extract the 
explanatory variables into a matrix and extract a response variable vector. In 
this example, the explanatory variables of interest will be 'cyl' (number of 
cylinder), and 'wt' (weight of vehicle) and the responding variable will be 
'mpg' (Miles/(US) gallon).

```{r}
##Extract X-> select cyl (column 2) and wt (column 6) variables
X=as.matrix(mtcars[c("cyl", "wt")])

##Extract y-> mpg (column 1)
y=as.vector(mtcars["mpg"])
```

To use the function 'linearReg':

The model of interest is: mpg = B0 + B1*cyl + B2*wt

```{r}
linearReg(y,X)
```

The summary of the 'lm()' function is very similar to 'linearReg' with a 
few exceptions:

1. 'linearReg' includes 95% Confidence Intervals and the input is a matrix
    and vector
2. 'lm()' includes Residual Standard Error and F-statistic information and 
    the input is a model formula

In comparison to summary of the 'lm()' function in the stats package:

```{r}
#original 'lm' function
model=lm(mpg~cyl+wt, data=mtcars)
summary(model)
```

The values that are shared within both function's outputs appear to be executed 
with the same amount of precision. The 'summary(lm())' function has the same 
output values as 'linearReg' only the values of the former are rounded to the
ten-thousandth decimal point.


To compare the efficiency between 'linearReg' and 'summary(lm())':

```{r}
system.time(linearReg(y,X))
system.time(summary(model))

bench::mark(linearReg(y,X))
bench::mark(summary(model))
```

The 'linearReg' function and 'summary(lm())' function appear to have similar 
system time elapses indicating similar efficiency. 'bench::mark()' isn't the 
best assessment of efficieny comparison because the 'linearReg' function runs
the linear regression and provides output, while the 'lm()' runs the linear 
regression and 'summary()' of the 'lm()' is jsut the output and therefore, the 
'summary(lm())' is expected to be slightly more efficient.
